---
title: ""
pagetitle: "About"
page-classes: hide-title
format:
  html:
    page-layout: full
    toc: false
---

<div class="page-banner" role="img" aria-label="Underwater banner video">
  <video autoplay muted loop playsinline preload="metadata">
    <source src="images/banners/about.mp4" type="video/mp4">
  </video>
  <div class="page-banner-overlay"></div>
  <div class="page-banner-inner" markdown="1">
# About Me {.page-banner-title}
<p class="page-banner-subtitle">marine science • painting • scientific videography</p>
  </div>
</div>

I’m **Jaden Orli**, a marine ecologist from **UCSB’s College of Creative Studies (Biology)**. I work at the seam of **field programs**, **population models**, and **public-facing communication** so decisions land with both **policymakers and communities**.

<div class="section-band section-professional" id="professional">
  <div class="band-inner">

## Professional

::: {.stacked-cards}

::: {.card}
### Fieldwork
<div class="metrics">
  <span class="pill">~350 dives</span>
  <span class="pill">≥75 scientific</span>
  <span class="pill">AAUS 60 ft</span>
  <span class="pill">Seine surveys</span>
  <span class="pill">Small-boat ops</span>
</div>

AAUS scientific diver in **kelp forests**; in **salt marsh** I lead/assist **seining and trap-based surveys**. Comfortable with tide windows, low-viz, and team logistics.

<details class="details-panel" markdown="1">
<summary>More Field Details</summary>

<div class="detail-stack">

<div class="detail-block detail-accent" markdown="1">
#### Current Program
**SONGS Mitigation Monitoring Program** *(Lab Technician, 2025 – present)*  
Intensive salt-marsh surveys for **fish and invertebrates** using **seines/traps**; careful **QA/QC** in the lab; gear maintenance and field safety; coordination with project scientists on long-term restoration monitoring.
</div>

<div class="detail-block" markdown="1">
#### Rocky Intertidal
**Kuris Lab and National Park Service (NPS):** transect surveys; species ID; tide-window planning; data entry and QA.
</div>

<div class="detail-block" markdown="1">
#### Kelp and Coastal Programs
- **PISCO / Caselle Lab:** underwater benthic and fish surveys (Northern Channel Islands)  
- **CCFRP:** hook-and-line surveys with volunteer anglers  
- **SB Coastal LTER:** kelp deployments/retrievals and site monitoring
</div>

<div class="detail-block" markdown="1">
#### Diving and Safety
Rescue, Nitrox, **AAUS (60 ft)**, Reef Check certification; night/low-viz/strong-current experience; task-loaded work (slates, cameras, etc).
</div>

</div><!-- /.detail-stack -->
</details>
:::

::: {.card}
### Modeling and Code
<div class="metrics">
  <span class="pill">Stage-structured</span>
  <span class="pill">Slot limits × MPAs</span>
  <span class="pill">Sobol + GLUE</span>
  <span class="pill">R + Quarto</span>
  <span class="pill">GIS / leaflet</span>
</div>

Two-sex, **stage-structured** lobster model; **VBGF** growth; size–fecundity; fishing applied **after projection** and only **outside MPAs**; scenario sweeps over **slot width × MPA coverage**.

<details class="details-panel" markdown="1">
<summary>More Modeling Details</summary>

<div class="detail-stack">

<div class="detail-block detail-accent" markdown="1">
#### Framework
Female-first stage matrix; optional male coupling; **exponential natural mortality**; quarterly `dt = 0.25`. Clean harvest accounting via post-projection survival in non-MPA cells → harvest = raw − fished trajectories.
</div>

<div class="detail-block" markdown="1">
#### Uncertainty and Robustness
- **Sobol (Salt)** global sensitivity to rank leverage parameters  
- **GLUE** ensembles to show plausible ranges, not just single fits  
- Reproducible **Quarto** reports; tidy pipelines; consistent figure styling
</div>

<div class="detail-block" markdown="1">
#### Geospatial and Other Projects
- **ArcGIS Pro / sf / terra / leaflet/tmap** for decision-ready maps  
- Spatial analyses: **IMTA aquaculture suitability** (U.S. West Coast EEZ); **Houston blackout** recovery patterns (equity lens)  
- Prior research: **Valentine Lab** (microbial hydrocarbon cycling; Bash + Bridges-2 PSC); **Novex Innovations** (sterile cell culture, SOP training)
</div>

</div><!-- /.detail-stack -->
</details>
:::

::: {.card}
### Policy and Community Engagement
<div class="metrics">
  <span class="pill">Science Communication</span>
  <span class="pill">Interactive Maps</span>
  <span class="pill">Citizen Science</span>
</div>

Outputs for **agencies, fishers, educators, and the public** — short explainers, interactive layers, and figures that surface uncertainty honestly.

<details class="details-panel" markdown="1">
<summary>More Engagement Details</summary>

<div class="detail-stack">

<div class="detail-block detail-accent" markdown="1">
#### Policy-Ready Outputs
Metrics aligned with decisions: biomass, spawning output, size structure, yield, stability; transparent assumptions. Plain-language scenarios—what changing **slot width** or **MPA coverage** means for effort and outcome.
</div>

<div class="detail-block" markdown="1">
#### Community-Facing Communication
- **Science videography** (60–120s): method explainers, field segments, and transparent communication with the public  
- **Pacific Manta Research Group:** citizen-science **photo-ID submission** site and diver education materials
</div>

<div class="detail-block" markdown="1">
#### Leadership and Media
- **Kuris Lab** project lead: fieldwork, student mentorship, conference talks (ESA, EEMB URS), **first-author manuscript in review**  
- **Environmental Media Production** (Assoc. Producer): filmed/edited a nonprofit climate program promo; on-location directing with a **Canon EOS C70**  
- Aquarium **Docent** experience translating conservation for the public
</div>

</div><!-- /.detail-stack -->
</details>

:::

<div class="links">
[Research](research.html){.read-more}[GitHub](https://github.com/jadenorli){.read-more}[Resume (PDF)](files/jaden_2025_resume.pdf){.read-more}
</div>

:::

  </div>
</div>

<!-- ========= PERSONAL ========= -->
<div class="section-band section-personal" id="personal">
  <div class="band-inner">

## Personal

::: {.stacked-cards}

::: {.card}
### Photography
<div class="metrics">
  <span class="pill">Texture and Pattern</span>
  <span class="pill">Motion and Mood</span>
  <span class="pill">Wildlife and Coastlines</span>
</div>

My photography lingers on details most people walk past — a kelp frond twisting in surge, coral polyps half-open, an alley washed in morning light. I look for **textures, moods, and small dramas** rather than single “perfect” shots. Marine photography becomes an exercise in noticing: subtle gradients in light, shadow, and texture that later make their way into my figures and color palettes.

<details class="details-panel" markdown="1">
<summary>More on Photography</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
**Themes** — kelp forest canopies, coral lattices, sand ripples, tidepool reflections, wreckage, and the geometry of fish schools.  
</div>

<div class="detail-block" markdown="1">
**Style** — high-contrast natural light, low-viz dives, and compositions that suggest movement or story — a shark’s turn, a crab emerging, a harbor just after rain.  
</div>

<div class="detail-block" markdown="1">
[See Photography →](photography.html)
</div>

</div><!-- /.detail-stack -->
</details>
:::

::: {.card}
### Painting 
<div class="metrics">
  <span class="pill">Wildlife Portraits</span>
  <span class="pill">Coastal Landscapes</span>
  <span class="pill">Mixed Media</span>
</div>

I paint to capture **place, memory, and personality** — a bay I swam in, a dog who wouldn’t sit still, a fish frozen mid-leap. Some works are observational; others are imagined worlds built from layers of field impressions.

<details class="details-panel" markdown="1">
<summary>More on Painting</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
**Mediums** — oil paint and mixed media  
</div>

<div class="detail-block" markdown="1">
**Subjects** — coastal bays, trout streams, personal places, and animals with a story to tell — sometimes literal, sometimes metaphorical.  
</div>

<div class="detail-block" markdown="1">
**Why it matters** — painting slows me down and lets me notice how light, pattern, and atmosphere really work. Those habits feed directly back into my figure design and scientific visualization.  
</div>

<div class="detail-block" markdown="1">
[See art →](art.html)
</div>

</div><!-- /.detail-stack -->
</details>
:::


::: {.card}
### Trails, Diving, and  Travel
<div class="metrics">
  <span class="pill">Coastal Hikes</span>
  <span class="pill">Night / Low-viz</span>
  <span class="pill">Working Harbors</span>
</div>

Most weekends I’m on a coastal trail or underwater; travel tends to follow coastlines and working harbors.

<details class="details-panel" markdown="1">
<summary>More on Trails and Travel</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
**Hiking** — coastal bluffs, estuary loops, and any trail that ends at a tidepool (with a pocket notebook for quick sketches).
</div>

<div class="detail-block" markdown="1">
**Diving** — kelp holdfasts, night dives, and low-viz marsh entries teach repeatable habits — useful in both field and code.
</div>

<div class="detail-block" markdown="1">
**Travel** — I gravitate to places where ecology, fisheries, and community sit close together — great training for policy conversations later.
</div>

</div><!-- /.detail-stack -->
</details>
:::

::: {.card}
### What I Value
<div class="metrics">
  <span class="pill">Clarity</span>
  <span class="pill">Reproducibility</span>
  <span class="pill">Field Reality</span>
</div>

Clarity over cleverness; field reality over assumptions; teams that surface uncertainty rather than hide it.

<details class="details-panel" markdown="1">
<summary>More on Values</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
- **Make it legible:** for managers, fishers, and the public  
- **Respect the process:** document assumptions, keep pipelines reproducible  
- **Stay curious:** bring field notes, photos, and sketches back into the model
</div>

</div><!-- /.detail-stack -->
</details>
:::
:::

  </div>
</div>

<!-- ========= DIVING ========= -->
<div class="section-band section-diving" id="diving">
  <div class="band-inner">

## Diving

::: {.stacked-cards}

::: {.card}
### Dive Map
<div class="metrics">
  <span class="pill">All Dives</span>
  <span class="pill">Scientific • Recreational • Training</span>
</div>

```{r, echo = FALSE, warning = FALSE, message = FALSE, eval = FALSE}
library(readr)
library(dplyr)
library(lubridate)
library(leaflet)
library(htmltools)

photo_dir <- "images/dives"

dives <- read_csv("data/dive_log.csv", show_col_types = FALSE) %>%
  rename(lat = latitude, lon = longitude) %>%
  mutate(
    category = tolower(trimws(category)),
    date_parsed  = suppressWarnings(mdy(date)),
    date_display = ifelse(!is.na(date_parsed), format(date_parsed, "%b %d, %Y"), ""),
    image_path = ifelse(!is.na(file) & nzchar(file), file.path(photo_dir, file), NA_character_)
  ) %>%
  # Keep ONLY these categories (no "other")
  filter(category %in% c("scientific","recreational","training")) %>%
  filter(!is.na(lat), !is.na(lon))

cat_cols <- c(
  scientific   = "#4D6C77",
  recreational = "#D1796B",
  training     = "#A3C3BD"
)

# Add explicit columns (avoids formula scoping weirdness)
dives <- dives %>%
  mutate(
    group = tools::toTitleCase(category),
    col   = unname(cat_cols[category])
  )

chip <- function(x) tags$span(class="dive-chip", x)

popup_card <- function(r){
  depth_m <- if (!is.na(r$max_depth_m)) round(r$max_depth_m, 1) else NA_real_
  depth_ft <- if (!is.na(depth_m)) round(depth_m * 3.28084, 0) else NA_real_

  chips <- list(
    if (nzchar(r$date_display)) chip(r$date_display) else NULL,
    chip(r$group),
    if (!is.na(depth_m)) chip(paste0("Max ", depth_m, " m (", depth_ft, " ft)")) else NULL,
    if (!is.na(r$bottom_time_min)) chip(paste0(r$bottom_time_min, " min")) else NULL
  )

  img_block <- if (!is.na(r$image_path) && nzchar(r$image_path)) {
    tags$a(href = r$image_path, `data-fancybox` = "dives",
           tags$img(src = r$image_path, class="dive-card__img"))
  } else NULL

  cap <- if ("caption" %in% names(r) && !is.na(r$caption) && nzchar(r$caption)) {
    tags$p(class="dive-card__caption", r$caption)
  } else NULL

  as.character(
    tags$div(class="dive-card",
      tags$h4(class="dive-card__title", r$site),
      tags$p(class="dive-card__sub", paste0(r$region, " • ", r$country)),
      tags$div(class="dive-card__meta", chips),
      cap,
      img_block
    )
  )
}

# ---- Custom cluster icons (THIS removes the default yellow/green) ----
cluster_icon_js <- JS("
function(cluster) {
  var count = cluster.getChildCount();

  // One unified cluster color (your soft coral tint)
  var c = '#688D8D';

  // size scales with count
  var size = (count < 10) ? 34 : (count < 50) ? 40 : 46;

  return new L.DivIcon({
    html:
      '<div class=\"dive-cluster\" style=\"' +
      'background:' + c + '; width:' + size + 'px; height:' + size + 'px;\">' +
      '<span>' + count + '</span></div>',
    className: 'dive-cluster-wrap',
    iconSize: [size, size]
  });
}
")


cluster_opts <- function(){
  markerClusterOptions(
    spiderfyOnMaxZoom = TRUE,
    showCoverageOnHover = FALSE,
    zoomToBoundsOnClick = TRUE,
    disableClusteringAtZoom = 7,
    iconCreateFunction = cluster_icon_js
  )
}



tiles <- providers$Esri.OceanBasemap

div(class="dive-map",
  {
    m <- leaflet(options = leafletOptions(scrollWheelZoom = FALSE)) %>%
      addProviderTiles(tiles)

    # 3 layers with separate cluster styling + overlay toggles (no "Other")
    for (cat in c("scientific","recreational","training")) {
      dat <- dives %>% filter(category == cat)
      if (nrow(dat) == 0) next

      m <- m %>%
        addCircleMarkers(
          data = dat,
          lng = ~lon, lat = ~lat,
          radius = 5.5,
          stroke = TRUE, weight = 1,
          color = ~col, fillColor = ~col,
          fillOpacity = 0.85,
          popup = lapply(seq_len(nrow(dat)), function(i) popup_card(dat[i, ])),
          group = tools::toTitleCase(cat),
          clusterOptions = cluster_opts()
        )
    }

    m %>%
      addLayersControl(
        overlayGroups = c("Scientific", "Recreational", "Training"),
        options = layersControlOptions(collapsed = FALSE)
      ) %>%
      addLegend(
        position = "bottomright",
        colors = unname(cat_cols),
        labels = tools::toTitleCase(names(cat_cols)),
        title = "Dive Type",
        opacity = 0.9
      ) %>%
      fitBounds(
        lng1 = min(dives$lon, na.rm = TRUE),
        lat1 = min(dives$lat, na.rm = TRUE),
        lng2 = max(dives$lon, na.rm = TRUE),
        lat2 = max(dives$lat, na.rm = TRUE)
      )
  }
)
```


```{r, echo = FALSE, warning = FALSE, message = FALSE}

# ── Packages ───────────────────────────────────────────────────────────────────
library(readr)
library(dplyr)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(lubridate)
library(jsonlite)

# ── Data ───────────────────────────────────────────────────────────────────────
photo_dir <- "images/dives"

dives <- read_csv("data/dive_log.csv", show_col_types = FALSE) %>%
  rename(lat = latitude, lon = longitude) %>%
  mutate(
    date_parsed  = mdy(date),
    year         = year(date_parsed),
    date_display = format(date_parsed, "%d %b %Y"),
    category     = tolower(trimws(category)),
    image_path   = ifelse(!is.na(file) & nzchar(file),
                          file.path(photo_dir, file), NA_character_)
  ) %>%
  filter(!is.na(lat), !is.na(lon)) %>%
  filter(category %in% c("scientific", "recreational", "training"))

# ── Palette — exact site CSS variables ────────────────────────────────────────
cat_colors <- c(
  scientific   = "#4D6C77",   # --marine-teal-3
  recreational = "#D1796B",   # --marine-coral
  training     = "#A3C3BD"    # --marine-teal-1
)
pal <- colorFactor(unname(cat_colors), levels = names(cat_colors))

# ── Popup builder ──────────────────────────────────────────────────────────────
make_popup <- function(r) {
  img_tag <- if (!is.na(r$image_path) && nzchar(r$image_path))
    sprintf('<img src="%s" class="dp-photo" alt="Dive photo at %s">',
            r$image_path, htmlEscape(r$site))
  else
    sprintf('<div class="dp-no-photo"><span>%s</span></div>',
            toupper(substr(r$site, 1, 2)))

  cap_tag <- if (!is.na(r$caption) && nzchar(r$caption))
    sprintf('<p class="dp-caption">%s</p>', htmlEscape(r$caption))
  else ""

  depth_tag <- if (!is.na(r$max_depth_m))
    sprintf('<span class="dp-chip">&#8595;&thinsp;%.0f m</span>', r$max_depth_m)
  else ""

  time_tag <- if (!is.na(r$bottom_time_min))
    sprintf('<span class="dp-chip">&#8986;&thinsp;%d min</span>',
            as.integer(r$bottom_time_min))
  else ""

  sprintf('
<div class="dive-popup">
  %s
  <div class="dp-body">
    <p class="dp-site">%s</p>
    <p class="dp-loc">%s &middot; %s</p>
    <p class="dp-date">%s</p>
    <div class="dp-chips">
      <span class="dp-chip dp-cat-%s">%s</span>
      <span class="dp-chip dp-yr">%d</span>
      %s %s
    </div>
    %s
  </div>
</div>',
    img_tag,
    htmlEscape(r$site),
    htmlEscape(r$region), htmlEscape(r$country),
    r$date_display,
    r$category, tools::toTitleCase(r$category),
    r$year,
    depth_tag, time_tag,
    cap_tag
  )
}

popups <- lapply(seq_len(nrow(dives)), function(i) make_popup(dives[i, ]))

# ── Summary statistics ─────────────────────────────────────────────────────────
n_total   <- nrow(dives)
n_ctry    <- n_distinct(dives$country)
n_sites   <- n_distinct(dives$site)
deepest   <- max(dives$max_depth_m, na.rm = TRUE)
hrs_total <- round(sum(dives$bottom_time_min, na.rm = TRUE) / 60)
yr_min    <- min(dives$year, na.rm = TRUE)
yr_max    <- max(dives$year, na.rm = TRUE)   # still needed for the year slider

# ── Custom cluster icon ────────────────────────────────────────────────────────
cluster_fn <- JS("function(cluster) {
  var n  = cluster.getChildCount();
  var sz = n < 10 ? 32 : n < 50 ? 40 : 50;
  return L.divIcon({
    html: '<div class=\"dm-cluster-bubble\" style=\"width:' + sz + 'px;height:' + sz + 'px\">' + n + '</div>',
    className: 'dm-cluster-wrap',
    iconSize: L.point(sz, sz)
  });
}")

cluster_opts <- markerClusterOptions(
  iconCreateFunction  = cluster_fn,
  showCoverageOnHover = FALSE,
  spiderfyOnMaxZoom   = TRUE,
  zoomToBoundsOnClick = TRUE,
  maxClusterRadius    = 50
)

# ── Build map (no addControl — panels live outside) ───────────────────────────
years <- sort(unique(dives$year))

m <- leaflet(options = leafletOptions(scrollWheelZoom = FALSE)) %>%
  addProviderTiles("Esri.WorldImagery",
                 options = providerTileOptions(opacity = 1)) %>%
  addProviderTiles("CartoDB.PositronOnlyLabels",
                 options = providerTileOptions(opacity = 0.65))

for (yr in years) {
  yr_dives  <- dives %>% filter(year == yr)
  yr_popups <- popups[dives$year == yr]

  m <- m %>% addCircleMarkers(
    data           = yr_dives,
    lng            = ~lon, lat = ~lat,
    radius         = 7,
    color          = ~pal(category),
    fillColor      = ~pal(category),
    fillOpacity    = 0.88,
    weight         = 2, opacity = 1,
    popup          = yr_popups,
    label          = ~site,
    labelOptions   = labelOptions(
      style     = list("font-family" = "inherit", "font-size" = "0.78rem",
                       "border-color" = "transparent", "padding" = "4px 8px"),
      direction = "auto"
    ),
    group          = as.character(yr),
    clusterOptions = cluster_opts
  )
}

m <- m %>%
  addLayersControl(
    overlayGroups = as.character(years),
    options       = layersControlOptions(collapsed = FALSE)
  ) %>%
  fitBounds(
    lng1 = min(dives$lon, na.rm = TRUE) - 4,
    lat1 = min(dives$lat, na.rm = TRUE) - 4,
    lng2 = max(dives$lon, na.rm = TRUE) + 4,
    lat2 = max(dives$lat, na.rm = TRUE) + 4
  )

# ── Inject popup CSS + year-filter JS via onRender ────────────────────────────
years_json <- toJSON(years, auto_unbox = FALSE)

m <- m %>% onRender(sprintf("
function(el, x) {
  var years = %s;

  /* hide the default layers control — JS slider drives visibility */
  var lc = document.querySelector('.leaflet-control-layers');
  if (lc) lc.style.display = 'none';

  var slider  = document.getElementById('dm-yr-slider');
  var display = document.getElementById('dm-yr-val');
  if (!slider || !display) return;

  function getLayerCheckboxes() {
    var out = {};
    document.querySelectorAll('.leaflet-control-layers-overlays label')
      .forEach(function(lbl) {
        var inp  = lbl.querySelector('input[type=checkbox]');
        var span = lbl.querySelector('span');
        var text = (span ? span.textContent : lbl.textContent).trim();
        if (inp) out[text] = inp;
      });
    return out;
  }

  function filterToYear(targetYr) {
    var cbs = getLayerCheckboxes();
    years.forEach(function(y) {
      var show = (targetYr === null || y === targetYr);
      var inp  = cbs[String(y)];
      if (inp && inp.checked !== show) inp.click();
    });
  }

  slider.addEventListener('input', function() {
    var yr = parseInt(this.value);
    display.textContent = yr;
    filterToYear(yr);
  });

  window.dmYrReset = function() {
    slider.value = slider.max;
    display.innerHTML = 'All years';
    filterToYear(null);
  };
}
", years_json))

# ── Assemble layout: sidebar (stats + filter) beside the map ──────────────────
stats_panel <- tags$div(class = "dm-stats-panel",
  tags$p(class = "dm-panel-head", "Dive Log"),
  tags$div(class = "dm-stat-grid",
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", n_total),
      tags$span(class = "dm-lbl", "dives")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", n_ctry),
      tags$span(class = "dm-lbl", "countries")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", n_sites),
      tags$span(class = "dm-lbl", "sites")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", HTML(sprintf("%.0f&thinsp;m", deepest))),
      tags$span(class = "dm-lbl", "deepest")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", HTML(sprintf("%d&thinsp;hr", hrs_total))),
      tags$span(class = "dm-lbl", "bottom time"))
  ),
  tags$div(class = "dm-legend",
    tags$span(class = "dm-dot", style = "background:#4D6C77"),
    "Scientific",
    tags$span(class = "dm-dot", style = "background:#D1796B"),
    "Recreational",
    tags$span(class = "dm-dot", style = "background:#A3C3BD"),
    "Training"
  )
)

filter_panel <- tags$div(class = "dm-filter-panel",
  tags$p(class = "dm-panel-head", "Filter by Year"),
  tags$p(class = "dm-yr-display", id = "dm-yr-val", HTML("All years")),
  tags$input(
    type  = "range", id = "dm-yr-slider",
    min   = yr_min, max = yr_max,
    step  = "1",    value = yr_max
  ),
  tags$button(id = "dm-yr-reset", onclick = "dmYrReset()", "Show All")
)

browsable(
  tags$div(class = "dive-map-layout",
    tags$div(class = "dive-map-sidebar",
      stats_panel,
      filter_panel
    ),
    tags$div(class = "dive-map-main",
      m
    )
  )
)
```

:::

:::

</div> </div>


<div class="coral-banner" markdown="1">
Regent Scholar • **Coastal Fund** major grants • Best Student Presentation (Int’l Conf. on Copepoda) • Best Student Poster (Southern Academy of Parasitologists) • Honorable Mention (WSN) • Manuscripts in review
</div>

<div class="gallery-footer">
  <a class="btn btn-primary" href="contact.html">Contact</a>
  <a class="read-more" href="#">Back to top</a>
</div>
