---
title: ""
pagetitle: "About"
---

<div class="page-banner" role="img" aria-label="Underwater banner video">
  <video autoplay muted loop playsinline preload="metadata">
    <source src="images/banners/about.mp4" type="video/mp4">
  </video>
  <div class="page-banner-overlay"></div>
  <div class="page-banner-inner" markdown="1">
# About Me {.page-banner-title}
<p class="page-banner-subtitle">marine science • painting • scientific videography</p>
  </div>
</div>

I’m **Jaden Orli**, a marine ecologist trained in biology at the **College of Creative Studies, University of California, Santa Barbara**. I work where **field programs**, **population models**, and **public-facing communication** meet, so that decisions land with both **policymakers and communities**.

<div class="section-band" id="professional">
  <div class="band-inner">

## Professional

::: {.stacked-cards}

::: {.card}
### Fieldwork
<div class="metrics">
  <span class="pill">~ 450 Dives</span>
  <span class="pill">~ 100 Scientific</span>
  <span class="pill">Certified to 60 Feet</span>
  <span class="pill">Seine Surveys</span>
  <span class="pill">Small-Boat Operations</span>
</div>

I dive kelp forests as a scientific diver certified by the **American Academy of Underwater Sciences (AAUS)**, and in **salt marsh** I lead and assist **seining and trap-based surveys**. I’m comfortable with tide windows, low visibility, and team logistics.

<details class="details-panel" markdown="1">
<summary>More Field Details</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
#### Recent Program
**San Onofre Nuclear Generating Station Mitigation Monitoring Program** *(Laboratory Technician, 2025 to 2026)*  
Intensive salt-marsh surveys for **fish and invertebrates** using **seines and traps**, careful **quality assurance and quality control** in the laboratory, gear maintenance and field safety, and coordination with project scientists on long-term restoration monitoring.
</div>

<div class="detail-block" markdown="1">
#### Rocky Intertidal
**Kuris Lab and the National Park Service:** transect surveys, species identification, tide-window planning, and data entry with quality assurance.
</div>

<div class="detail-block" markdown="1">
#### Kelp and Coastal Programs
- **Partnership for Interdisciplinary Studies of Coastal Oceans (PISCO), Caselle Lab:** underwater benthic and fish surveys in the Northern Channel Islands  
- **California Collaborative Fisheries Research Program (CCFRP):** hook-and-line surveys with volunteer anglers  
- **Santa Barbara Coastal Long Term Ecological Research (SBC LTER):** kelp deployments and retrievals, and site monitoring
</div>

<div class="detail-block" markdown="1">
#### Diving and Safety
Rescue and Nitrox certifications, **American Academy of Underwater Sciences (AAUS) certification to 60 feet**, and Reef Check certification. Experience with night dives, low visibility, and strong current, and with task-loaded work carrying slates, cameras, and other equipment.
</div>

</div>
</details>
:::

::: {.card}
### Modeling and Code
<div class="metrics">
  <span class="pill">Stage-Structured</span>
  <span class="pill">Slot Limits and MPAs</span>
  <span class="pill">Sensitivity and Uncertainty</span>
  <span class="pill">Geospatial Mapping</span>
</div>

A two-sex, **stage-structured** lobster model with **von Bertalanffy** growth and a size-to-fecundity relationship. Fishing is applied **after projection** and only **outside marine protected areas (MPAs)**, with scenario sweeps across **slot width and marine protected area coverage**.

<details class="details-panel" markdown="1">
<summary>More Modeling Details</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
#### Framework
A female-first stage matrix with optional male coupling, **exponential natural mortality**, and quarterly time steps of `dt = 0.25`. Harvest is accounted for cleanly through post-projection survival in cells outside marine protected areas, so that harvest is the difference between the raw and the fished trajectories.
</div>

<div class="detail-block" markdown="1">
#### Uncertainty and Robustness
- **Sobol global sensitivity analysis**, run with the Salt package, to rank which parameters carry the most leverage  
- **Generalized Likelihood Uncertainty Estimation** ensembles, to show plausible ranges rather than a single fit  
- Reproducible **Quarto** reports, tidy pipelines, and consistent figure styling
</div>

</div>
</details>
:::

::: {.card}
### Policy and Community Engagement
<div class="metrics">
  <span class="pill">Science Communication</span>
  <span class="pill">Interactive Maps</span>
  <span class="pill">Citizen Science</span>
</div>

Outputs for **agencies, fishers, educators, and the public**: short explainers, interactive layers, and figures that surface uncertainty honestly.

<details class="details-panel" markdown="1">
<summary>More Engagement Details</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
#### Policy-Ready Outputs
Metrics aligned with decisions: biomass, spawning output, size structure, yield, and stability, with transparent assumptions throughout. Plain-language scenarios showing what changing **slot width** or **marine protected area coverage** means for effort and outcome.
</div>

<div class="detail-block" markdown="1">
#### Community-Facing Communication
- **Science videography**, 60 to 120 seconds: method explainers, field segments, and transparent communication with the public  
- **Pacific Manta Research Group:** a citizen-science **photo identification submission** site and diver education materials
</div>

<div class="detail-block" markdown="1">
#### Leadership and Media
- **Kuris Lab** project lead: fieldwork, student mentorship, conference talks at the Ecological Society of America and at the Ecology, Evolution, and Marine Biology Undergraduate Research Symposium, and a **first-author manuscript in review**  
- **Environmental Media Production**, as Associate Producer: filmed and edited a promotional piece for a nonprofit climate program, and directed on location with a **Canon EOS C70**  
- Aquarium **Docent** experience translating conservation for the public
</div>

</div>
</details>

:::

<div class="links">
[Research](research.html){.read-more}[GitHub](https://github.com/jadenorli){.read-more}[Resume (PDF)](files/jaden_2026_resume.pdf){.read-more}
</div>

:::

  </div>
</div>


<!-- ========= DIVING ========= -->
<div class="section-band" id="diving">
  <div class="band-inner">

## Diving

::: {.stacked-cards}

::: {.card}
### Dive Map
<div class="metrics">
  <span class="pill">All Dives</span>
  <span class="pill">Scientific</span>
  <span class="pill">Recreational</span>
</div>

```{r, echo = FALSE, warning = FALSE, message = FALSE}

# ── Packages ───────────────────────────────────────────────────────────────────
library(readr)
library(dplyr)
library(leaflet)
library(htmltools)
library(htmlwidgets)
library(lubridate)
library(tidyr)
library(jsonlite)

# ── Data ───────────────────────────────────────────────────────────────────────
photo_dir <- "images/dives"

dives <- read_csv("data/dive_log.csv", show_col_types = FALSE) %>%
  rename(lat = latitude, lon = longitude) %>%
  mutate(
    date_parsed  = mdy(date),
    year         = year(date_parsed),
    date_display = format(date_parsed, "%d %b %Y"),
    category     = tolower(trimws(category)),
    image_path   = ifelse(!is.na(file) & nzchar(file),
                          file.path(photo_dir, file), NA_character_)
  ) %>%
  filter(!is.na(lat), !is.na(lon)) %>%
  filter(category %in% c("scientific", "recreational", "training")) %>%
  mutate(
    # A dive can belong to more than one category: the PISCO training dives in
    # the 2024 season were scientific work AND training. `category` stays
    # single-valued because the map's layer groups are built from it, and
    # `tags` carries the full set, semicolon separated.
    tags = ifelse(is.na(tags) | !nzchar(tags), category, tags)
  )

# TRUE when a dive carries the given tag, whether or not it is that dive's
# primary category. Counts and layer membership both run through this, so a
# cross-listed dive appears under both buttons rather than being forced to pick.
has_tag <- function(d, tag) grepl(tag, d$tags, fixed = TRUE)

# ── Palette ────────────────────────────────────────────────────────────────────
cat_colors <- c(
  scientific   = "#4D6C77",
  recreational = "#D1796B",
  training  = "#A3C3BD",
  "advanced placement"  = "#7A8B99"
)
pal <- colorFactor(unname(cat_colors), levels = names(cat_colors))

# ── Popup builder ──────────────────────────────────────────────────────────────
make_popup <- function(r) {
  img_tag <- if (!is.na(r$image_path) && nzchar(r$image_path))
    sprintf('<img src="%s" class="dp-photo" alt="Dive photo at %s">',
            r$image_path, htmlEscape(r$site))
  else
    sprintf('<div class="dp-no-photo"><span>%s</span></div>',
            toupper(substr(r$site, 1, 2)))

  cap_tag <- if (!is.na(r$caption) && nzchar(r$caption))
    sprintf('<p class="dp-caption">%s</p>', htmlEscape(r$caption))
  else ""

  depth_tag <- if (!is.na(r$max_depth_m))
    sprintf('<span class="dp-chip">&#8595;&thinsp;%.0f m</span>', r$max_depth_m)
  else ""

  time_tag <- if (!is.na(r$bottom_time_min))
    sprintf('<span class="dp-chip">&#8986;&thinsp;%d min</span>',
            as.integer(r$bottom_time_min))
  else ""

  sprintf('
<div class="dive-popup">
  %s
  <div class="dp-body">
    <p class="dp-site">%s</p>
    <p class="dp-loc">%s &middot; %s</p>
    <p class="dp-date">%s</p>
    <div class="dp-chips">
      <span class="dp-chip dp-cat-%s">%s</span>
      <span class="dp-chip dp-yr">%d</span>
      %s %s
    </div>
    %s
  </div>
</div>',
    img_tag,
    htmlEscape(r$site),
    htmlEscape(r$region), htmlEscape(r$country),
    r$date_display,
    r$category, tools::toTitleCase(r$category),
    r$year,
    depth_tag, time_tag,
    cap_tag
  )
}

popups <- lapply(seq_len(nrow(dives)), function(i) make_popup(dives[i, ]))

# ── Summary statistics ─────────────────────────────────────────────────────────
n_total   <- nrow(dives)
n_ctry    <- n_distinct(dives$country)
n_sites   <- n_distinct(dives$site)
deepest   <- max(dives$max_depth_m, na.rm = TRUE)
hrs_total <- round(sum(dives$bottom_time_min, na.rm = TRUE) / 60)
yr_min    <- min(dives$year, na.rm = TRUE)
yr_max    <- max(dives$year, na.rm = TRUE)

# ── Per-category counts for button labels ──────────────────────────────────────
n_sci <- sum(has_tag(dives, "scientific"))
n_rec <- sum(has_tag(dives, "recreational"))
n_tra <- sum(has_tag(dives, "training"))

# ── Dives by program, grouped under their category ─────────────────────────────
# Straight from the program column in the dive log, so this never goes stale:
# add a program to the CSV and it appears under the right button on the next
# render. capacity separates paid work from volunteering, which program alone
# cannot say.
prog_by_cat <- dives %>%
  filter(!is.na(program), nzchar(program)) %>%
  tidyr::separate_rows(tags, sep = ";") %>%
  rename(cat_tag = tags) %>%
  count(cat_tag, program, sort = TRUE)

n_paid <- sum(dives$capacity == "employed",  na.rm = TRUE)
n_vol  <- sum(dives$capacity == "volunteer", na.rm = TRUE)

# One <details> disclosure per category, holding that category's programs.
# Returns NULL when a category has no programs, and NULL entries drop out of
# the tag list, so recreational simply gets no dropdown.
prog_details <- function(cat) {
  rows <- prog_by_cat %>% filter(cat_tag == cat) %>% arrange(desc(n))
  if (nrow(rows) == 0) return(NULL)
  tags$details(class = "dm-prog",
    tags$summary(sprintf("Programs (%d)", nrow(rows))),
    tags$ul(class = "dm-prog-list",
      lapply(seq_len(nrow(rows)), function(i)
        tags$li(
          tags$span(class = "dm-prog-name", rows$program[i]),
          tags$span(class = "dm-prog-n",    rows$n[i])
        ))
    ),
    if (cat == "scientific")
      tags$p(class = "dm-prog-note",
             sprintf("%d paid, %d volunteer", n_paid, n_vol))
  )
}

# ── Custom cluster icons, one per category color ──────────────────────────────
make_cluster_fn <- function(hex) {
  JS(sprintf("function(cluster) {
    var n   = cluster.getChildCount();
    var sz  = n < 10 ? 32 : n < 50 ? 40 : 50;
    var col = '%s';
    return L.divIcon({
      html: '<div class=\"dm-cluster-bubble\" style=\"width:' + sz + 'px;height:' + sz + 'px;background:' + col + '\">' + n + '</div>',
      className: 'dm-cluster-wrap',
      iconSize: L.point(sz, sz)
    });
  }", hex))
}

# maxClusterRadius = 60 (up from 50) reduces visual collision between
# overlapping clusters from different categories at the same location
cluster_opts_by_cat <- list(
  scientific   = markerClusterOptions(iconCreateFunction = make_cluster_fn("#4D6C77"),
                                      showCoverageOnHover = FALSE, spiderfyOnMaxZoom = TRUE,
                                      zoomToBoundsOnClick = TRUE, maxClusterRadius = 60),
  recreational = markerClusterOptions(iconCreateFunction = make_cluster_fn("#D1796B"),
                                      showCoverageOnHover = FALSE, spiderfyOnMaxZoom = TRUE,
                                      zoomToBoundsOnClick = TRUE, maxClusterRadius = 60),
  training     = markerClusterOptions(iconCreateFunction = make_cluster_fn("#A3C3BD"),
                                      showCoverageOnHover = FALSE, spiderfyOnMaxZoom = TRUE,
                                      zoomToBoundsOnClick = TRUE, maxClusterRadius = 60)
)

# ── Build map ──────────────────────────────────────────────────────────────────
years      <- sort(unique(dives$year))
categories <- c("scientific", "recreational", "training")

all_groups <- as.vector(outer(as.character(years), categories,
                               FUN = function(y, c) paste0(y, "_", c)))

# scrollWheelZoom = "center" enables scroll-zoom only when the cursor is near
# the map center. Prevents the map hijacking normal page scrolling
m <- leaflet(width = "100%", height = "100%",
             options = leafletOptions(scrollWheelZoom = "center")) %>%
  addProviderTiles("Esri.WorldImagery",
                   options = providerTileOptions(opacity = 1)) %>%
  addProviderTiles("CartoDB.PositronOnlyLabels",
                   options = providerTileOptions(opacity = 0.65))

for (yr in years) {
  for (cat in categories) {
    keep    <- dives$year == yr & has_tag(dives, cat)
    sub     <- dives[keep, ]
    if (nrow(sub) == 0) next
    sub_pop <- popups[keep]
    grp     <- paste0(yr, "_", cat)

    m <- m %>% addCircleMarkers(
      data           = sub,
      lng            = ~lon, lat = ~lat,
      radius         = 7,
      color          = ~pal(category),
      fillColor      = ~pal(category),
      fillOpacity    = 0.88,
      weight         = 2, opacity = 1,
      popup          = sub_pop,
      label          = ~site,
      labelOptions   = labelOptions(
        style     = list("font-family" = "inherit", "font-size" = "0.78rem",
                         "border-color" = "transparent", "padding" = "4px 8px"),
        direction = "auto"
      ),
      group          = grp,
      clusterOptions = cluster_opts_by_cat[[cat]]
    )
  }
}

m <- m %>%
  addLayersControl(
    overlayGroups = all_groups,
    options       = layersControlOptions(collapsed = FALSE)
  ) %>%
  fitBounds(
    lng1 = min(dives$lon, na.rm = TRUE) - 4,
    lat1 = min(dives$lat, na.rm = TRUE) - 4,
    lng2 = max(dives$lon, na.rm = TRUE) + 4,
    lat2 = max(dives$lat, na.rm = TRUE) + 4
  )

# ── JS: year slider + category buttons ────────────────────────────────────────
years_json <- toJSON(years,      auto_unbox = FALSE)
cats_json  <- toJSON(categories, auto_unbox = FALSE)

m <- m %>% onRender(sprintf("
function(el, x) {
  var map        = this;
  var years      = %s;
  var categories = %s;

  /* ── Hide native layers control ── */
  var lc = document.querySelector('.leaflet-control-layers');
  if (lc) lc.style.display = 'none';

  /* ── Mobile: force size recalc ── */
  function fixSize() { map.invalidateSize({ animate: false }); }
  setTimeout(fixSize, 100);
  setTimeout(fixSize, 400);
  setTimeout(fixSize, 1000);
  window.addEventListener('resize', function() { setTimeout(fixSize, 150); });

  /* ── State: which years/cats are active ── */
  var activeYear = null;
  var activeCats = { scientific: true, recreational: true, training: true };

  /* ── Get the hidden checkbox for a group name ── */
  function getCheckboxes() {
    var out = {};
    document.querySelectorAll('.leaflet-control-layers-overlays label')
      .forEach(function(lbl) {
        var inp  = lbl.querySelector('input[type=checkbox]');
        var span = lbl.querySelector('span');
        var text = (span ? span.textContent : lbl.textContent).trim();
        if (inp) out[text] = inp;
      });
    return out;
  }

  /* ── Apply both filters together ── */
  function applyFilters() {
    var cbs = getCheckboxes();
    years.forEach(function(y) {
      categories.forEach(function(c) {
        var grp       = y + '_' + c;
        var yearMatch = (activeYear === null || y === activeYear);
        var catMatch  = activeCats[c];
        var show      = yearMatch && catMatch;
        var inp       = cbs[grp];
        if (inp && inp.checked !== show) inp.click();
      });
    });
  }

  /* ── Year slider ── */
  var slider  = document.getElementById('dm-yr-slider');
  var display = document.getElementById('dm-yr-val');

  if (slider && display) {
    slider.addEventListener('input', function() {
      activeYear = parseInt(this.value);
      display.textContent = activeYear;
      applyFilters();
    });

    window.dmYrReset = function() {
      activeYear = null;
      slider.value = slider.max;
      display.innerHTML = 'All years';
      applyFilters();
    };
  }

  /* ── Category buttons ── */
  var catBtns = document.querySelectorAll('.dm-cat-btn');
  catBtns.forEach(function(btn) {
    btn.addEventListener('click', function() {
      var cat = this.dataset.cat;
      activeCats[cat] = !activeCats[cat];
      this.classList.toggle('dm-cat-btn--off', !activeCats[cat]);
      applyFilters();
    });
  });
}
", years_json, cats_json))

# ── Sidebar panels ─────────────────────────────────────────────────────────────
stats_panel <- tags$div(class = "dm-stats-panel",
  tags$p(class = "dm-panel-head", "Dive Log"),
  tags$div(class = "dm-stat-grid",
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", n_total),
      tags$span(class = "dm-lbl", "dives")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", n_ctry),
      tags$span(class = "dm-lbl", "countries")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", n_sites),
      tags$span(class = "dm-lbl", "sites")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", HTML(sprintf("%.0f&thinsp;m", deepest))),
      tags$span(class = "dm-lbl", "deepest")),
    tags$div(class = "dm-stat",
      tags$span(class = "dm-num", HTML(sprintf("%d&thinsp;hr", hrs_total))),
      tags$span(class = "dm-lbl", "bottom time"))
  )
)

# Category filter panel, with counts shown on each button
# Each category is a button (which filters the map) followed by its own
# dropdown of programs. The button and the disclosure are siblings rather than
# nested, because a <details> inside a <button> is invalid HTML and browsers
# handle it unpredictably.
cat_block <- function(cat, label, n, hex) {
  tags$div(class = "dm-cat-block",
    tags$button(class = "dm-cat-btn", `data-cat` = cat,
      tags$span(class = "dm-cat-dot", style = sprintf("background:%s", hex)),
      sprintf("%s (%d)", label, n)),
    prog_details(cat)
  )
}

cat_panel <- tags$div(class = "dm-filter-panel",
  tags$p(class = "dm-panel-head", "Filter by Type"),
  tags$div(class = "dm-cat-btns",
    cat_block("scientific",   "Scientific",   n_sci, "#4D6C77"),
    cat_block("recreational", "Recreational", n_rec, "#D1796B"),
    cat_block("training",     "Training",     n_tra, "#A3C3BD")
  )
)

filter_panel <- tags$div(class = "dm-filter-panel",
  tags$p(class = "dm-panel-head", "Filter by Year"),
  tags$p(class = "dm-yr-display", id = "dm-yr-val", HTML("All years")),
  tags$input(
    type  = "range", id = "dm-yr-slider",
    min   = yr_min, max = yr_max,
    step  = "1",    value = yr_max
  ),
  tags$button(id = "dm-yr-reset", onclick = "dmYrReset()", "Show All")
)

# ── Inline CSS, needed because browsable() renders inside an iframe ───────────
# The page's styles.css is not loaded inside the widget iframe, so all
# dive-map styles must travel with the widget as a <style> tag.
inline_css <- tags$style(HTML("
  *,*::before,*::after{box-sizing:border-box;}
  body{margin:0;font-family:'Inter',system-ui,sans-serif;}

  .dive-map-layout{display:flex;gap:1rem;align-items:stretch;width:100%;}
  .dive-map-sidebar{display:flex;flex-direction:column;gap:.75rem;flex:0 0 190px;min-width:0;}
  .dive-map-main{
    flex:1 1 0;min-width:0;position:relative;min-height:460px;
  }
  /* align-items:stretch makes this column as tall as the sidebar, whatever the
     sidebar ends up being. The widget is then pinned to all four edges of it,
     so the map matches the filters instead of sitting at a fixed height with
     white space beneath. min-height is the floor for the case where the
     sidebar is short. */
  .dive-map-main .html-widget,
  .dive-map-main .leaflet{
    position:absolute !important;inset:0;
    width:100% !important;height:100% !important;
  }

  .dm-stats-panel,.dm-filter-panel{
    background:#fff;
    border:1px solid #e5e7eb;
    border-radius:.75rem;
    padding:.85rem 1rem;
    box-shadow:0 3px 12px rgba(0,0,0,.06);
    font-family:'Inter',system-ui,sans-serif;
  }
  .dm-stats-panel{border-top:3px solid #4D6C77;}
  .dm-filter-panel{border-top:3px solid #A3C3BD;}

  .dm-panel-head{
    margin:0 0 .6rem;font-size:.62rem;font-weight:700;
    letter-spacing:.10em;text-transform:uppercase;color:#2E3C43;
  }
  .dm-stat-grid{display:grid;grid-template-columns:repeat(2,1fr);gap:.5rem .25rem;margin-bottom:.7rem;}
  .dm-stat{display:flex;flex-direction:column;align-items:center;line-height:1.2;}
  .dm-num{font-size:.92rem;font-weight:700;color:#4D6C77;}
  .dm-lbl{font-size:.58rem;color:#9ca3af;text-align:center;}

  .dm-cat-btns{display:flex;flex-direction:column;gap:.4rem;}
  .dm-cat-btn{
    display:flex;align-items:center;gap:.5rem;width:100%;
    padding:.4rem .65rem;border:1.5px solid #e5e7eb;border-radius:.5rem;
    background:#fff;color:#2E3C43;font-family:'Inter',system-ui,sans-serif;
    font-size:.75rem;font-weight:600;cursor:pointer;text-align:left;
    transition:background .15s,opacity .15s,border-color .15s;
  }
  .dm-cat-btn:hover{background:#E6F1F5;border-color:#688D8D;}
  .dm-cat-btn--off{opacity:.4;background:#f8f8f8;}
  .dm-cat-dot{width:9px;height:9px;border-radius:50%;display:inline-block;flex-shrink:0;}

  .dm-yr-display{font-size:1.1rem;font-weight:700;color:#4D6C77;margin:0 0 .55rem;line-height:1;}
  #dm-yr-slider{
    -webkit-appearance:none;appearance:none;width:100%;height:4px;
    border-radius:4px;background:#E6F1F5;outline:none;display:block;
    margin-bottom:.6rem;accent-color:#4D6C77;
  }
  #dm-yr-slider::-webkit-slider-thumb{
    -webkit-appearance:none;width:15px;height:15px;border-radius:50%;
    background:#4D6C77;cursor:pointer;box-shadow:0 1px 4px rgba(0,0,0,.20);border:2px solid #fff;
  }
  #dm-yr-reset{
    font-size:.66rem;padding:4px 0;width:100%;
    border:1.5px solid #4D6C77;border-radius:6px;background:transparent;
    color:#4D6C77;cursor:pointer;font-family:inherit;letter-spacing:.04em;
    transition:background .15s,color .15s;
  }
  #dm-yr-reset:hover{background:#4D6C77;color:#fff;}

  .dive-map-main .leaflet-container{
    height:100% !important;border-radius:14px;
    border:1px solid #e5e7eb;box-shadow:0 6px 22px rgba(0,0,0,.06);overflow:hidden;
  }
  @media (max-width:760px){
    .dive-map-layout{flex-direction:column;}
    .dive-map-sidebar{flex:none;width:100%;flex-direction:row;flex-wrap:wrap;}
    .dm-stats-panel,.dm-filter-panel{flex:1 1 200px;}
    .dive-map-main{width:100%;min-height:380px;height:380px;}
    .dive-map-main .leaflet-container{height:380px !important;}
  }
  @media (max-width:600px){
    .dive-map-main{height:360px;min-height:360px;}
    .dive-map-main .leaflet-container{height:360px !important;}
  }

  .dive-map-main .leaflet-popup-content-wrapper{
    padding:0 !important;border-radius:12px !important;overflow:hidden;
    box-shadow:0 6px 22px rgba(0,0,0,.16) !important;border:1px solid #e5e7eb;
  }
  .dive-map-main .leaflet-popup-tip-container{display:none;}
  .dive-map-main .leaflet-popup-content{margin:0 !important;width:auto !important;}
  .dive-map-main .leaflet-popup-close-button{
    top:6px !important;right:8px !important;color:rgba(255,255,255,.85) !important;
    font-size:1.1rem !important;text-shadow:0 1px 3px rgba(0,0,0,.4);z-index:10;
  }
  .dive-popup{font-family:'Inter',system-ui,sans-serif;width:240px;}
  .dp-photo{width:100%;height:145px;object-fit:cover;display:block;}
  .dp-no-photo{
    width:100%;height:72px;
    background:linear-gradient(135deg,#4D6C77 0%,#2E3C43 100%);
    display:flex;align-items:center;justify-content:center;
  }
  .dp-no-photo span{font-size:1.5rem;font-weight:700;color:rgba(255,255,255,.3);letter-spacing:.05em;}
  .dp-body{padding:10px 13px 13px;}
  .dp-site{margin:0 0 2px;font-size:.96rem;font-weight:700;color:#2E3C43;}
  .dp-loc{margin:0 0 1px;font-size:.73rem;color:#43535B;}
  .dp-date{margin:0 0 7px;font-size:.68rem;color:#9ca3af;}
  .dp-chips{display:flex;flex-wrap:wrap;gap:4px;margin-bottom:5px;}
  .dp-chip{
    font-size:.67rem;padding:2px 8px;border-radius:20px;
    background:#F5F7F9;color:#43535B;border:1px solid #e5e7eb;
  }
  .dp-yr{background:#E6F1F5;color:#4D6C77;}
  .dp-cat-scientific{background:#dde8ec;color:#4D6C77;}
  .dp-cat-recreational{background:#f5e4e2;color:#D1796B;}
  .dp-cat-training{background:#e4efed;color:#688D8D;}
  .dp-caption{margin:4px 0 0;font-size:.73rem;color:#43535B;font-style:italic;}
  .dm-cat-block{display:flex;flex-direction:column;gap:.25rem;}

  .dm-prog{margin:0 0 .1rem;}
  .dm-prog summary{
    list-style:none;cursor:pointer;
    padding:.15rem .2rem .15rem 1.45rem;
    font-size:.64rem;letter-spacing:.05em;text-transform:uppercase;
    color:#688D8D;font-weight:700;position:relative;
  }
  .dm-prog summary::-webkit-details-marker{display:none;}
  .dm-prog summary::before{
    content:'';position:absolute;left:.55rem;top:.42rem;
    width:.32rem;height:.32rem;
    border-right:1.5px solid #688D8D;border-bottom:1.5px solid #688D8D;
    transform:rotate(45deg);transition:transform .18s ease;
  }
  .dm-prog[open] summary::before{transform:rotate(-135deg);top:.5rem;}
  .dm-prog > ul{margin-left:1.45rem;}

  .dm-prog-list{list-style:none;margin:0;padding:0;}
  .dm-prog-list li{
    display:flex;justify-content:space-between;gap:.5rem;
    padding:.3rem 0;font-size:.72rem;color:#43535B;
    border-top:1px solid #f1f3f5;
  }
  .dm-prog-list li:first-child{border-top:0;}
  .dm-prog-n{font-weight:700;color:#4D6C77;}
  .dm-prog-note{
    margin:.4rem 0 0 1.45rem;padding-top:.35rem;border-top:1px solid #f1f3f5;
    font-size:.6rem;letter-spacing:.04em;text-transform:uppercase;
    color:#9ca3af;
  }

  .dm-cluster-wrap{background:transparent !important;border:none !important;}
  .dm-cluster-bubble{
    border-radius:50%;color:#fff;display:flex;align-items:center;justify-content:center;
    font-weight:700;font-size:.8rem;letter-spacing:-.02em;
    box-shadow:0 2px 8px rgba(0,0,0,.22);border:2px solid rgba(255,255,255,.75);
    font-family:'Inter',system-ui,sans-serif;
  }
"))

browsable(
  tagList(
    inline_css,
    tags$div(class = "dive-map-layout",
      tags$div(class = "dive-map-sidebar",
        stats_panel,
        cat_panel,
        filter_panel
      ),
      tags$div(class = "dive-map-main",
        m
      )
    )
  )
)
```

:::

:::

</div> 
</div>

<!-- ========= TIMELINE ========= -->
<div class="section-band" id="timeline">
  <div class="band-inner">

## Timeline

From an aquarium volunteer at fifteen to coral reefs and fisheries models: every role I've held, colored by the world it belongs to. Hover any bar for details.

<div class="jtl-card">
<div class="jtl-wrap">
<p class="jtl-cap"><strong>Each color is a different world I worked in</strong>, and they overlap and double back more than you might expect. Click any group on the left to show or hide it.</p>
<div class="jtl-chart"></div>
</div>
</div>

<script>
(function(){
  var SEC={scicomm:["Science Communication and Outreach","#D1796B"],industry:["Industry","#C08A3E"],academia:["Academia","#3E6E86"],nonprofit:["Nonprofit and Citizen Science","#5E8D7E"],regulatory:["Regulatory and Mitigation","#6D6A9C"]};
  var ORDER=["scicomm","industry","academia","nonprofit","regulatory"];
  var E=[
    ["scicomm","Greensboro Science Center","Greensboro Science Center","Aquarium Docent",2018.08,2021.67,"February 2018 to August 2021",false],
    ["scicomm","Ecological Modeling Course","Ecological Modeling Course","Undergraduate Teaching Assistant",2024.00,2024.25,"January 2024 to March 2024",false],
    ["scicomm","Environmental Media Production","Environmental Media Production","Associate Producer",2025.17,2025.33,"March 2025 to April 2025",false],
    ["industry","Novex Innovations","Novex Innovations","Laboratory Technician, stem-cell research and development",2020.67,2021.67,"August 2020 to August 2021",false],
    ["academia","Floge Lab","Floge Marine Microbial Ecology Lab","Research Intern",2020.00,2020.25,"January 2020 to March 2020",false],
    ["academia","Kuris Parasite Ecology Lab","Kuris Parasite Ecology Lab","Project Lead, first-author paper",2021.67,2026.25,"September 2021 to March 2026",false],
    ["academia","Valentine Lab","Valentine Lab","Research Intern, sediment coring cruise and bioinformatics training",2023.00,2025.67,"January 2023 to August 2025",false],
    ["academia","Santa Barbara Coastal LTER","Santa Barbara Coastal Long Term Ecological Research","Scientific Diver",2023.17,2024.42,"March 2023 to May 2024",false],
    ["academia","Caselle Lab","Partnership for Interdisciplinary Studies of Coastal Oceans (Caselle Lab)","Scientific Diver",2024.42,2024.83,"June 2024 to October 2024",false],
    ["academia","Ocean Recoveries Lab","Stier Ocean Recoveries Lab","Staff Research Associate, current role",2024.67,2026.68,"September 2024 to present",true],
    ["nonprofit","Pacific Manta Research Group (PMRG)","Pacific Manta Research Group","Research Intern and Web Designer",2021.92,2024.00,"December 2021 to January 2024",false],
    ["nonprofit","Reef Check California","Reef Check California","Intern and Scientific Diver",2022.42,2023.25,"June 2022 to April 2023",false],
    ["regulatory","SONGS Mitigation Monitoring Program","San Onofre Nuclear Generating Station Mitigation Monitoring Program","Laboratory Assistant",2025.67,2026.00,"August 2025 to January 2026",false]
  ];
  var MS=[[2020.42,"Graduated High School (Reagan High School)",1,false],[2022.17,"Scientific Diver Certification (AAUS)",2,false],[2025.42,"Finished Undergraduate Degree (UCSB)",1,false],[2025.95,"First Publications",3,true]];
  var FUT=null; 
  // T1 and RIGHT_PAD together decide how many pixels a year is worth: the
  // track is the chart width less the legend gutter and the right pad, divided
  // by T1 minus T0. Both were trimmed to widen the years by about a tenth,
  // T1 from 2027.5 and RIGHT_PAD from 150. The pad is only there to stop the
  // track running to the chart edge, not to reserve room for the names beside
  // the last bars, which are allowed to use the full chart width and are
  // checked against it in placeLabels.
  var T0=2018.0,T1=2027.2,NOW=2026.68,LABEL_W=225,PILL_M=20,RIGHT_PAD=95,RIBBON_H=145,ROW_H=24,ROW_GAP=5,LANE_GAP=16,LANES_TOP=RIBBON_H+8,AXIS_H=28;
  // Strip below the year axis for the undergraduate caption, which used to
  // sit inside the shaded band and is now a caption under the chart.
  var CAP_H=30;
  // How close an outside name may come to a vertical rule before it counts as
  // running into it. A rule is 2px wide, so 12 leaves five clear pixels on
  // either side. It was 6, which was enough to keep the letters off the rule
  // arithmetically but left them close enough to read as touching.
  var NOW_CLEAR=12;
  function msTop(t){return t===3?12:(t===2?54:96);}
  // Which sectors are currently drawn. The left-hand legend toggles these.
  // Declared out here rather than inside render() so that a resize redraw,
  // which calls render() again, keeps whatever filter is showing.
  var ACTIVE={}; ORDER.forEach(function(k){ACTIVE[k]=true;});
  // Floor on lane height. Every pill is a fixed 52px tall (see .jtl-lane in
  // §24) and a one-row lane is only 24px, so without a floor the pill for a
  // short lane would overlap its neighbour. It also doubles as the height a
  // lane collapses to when switched off: not zero, because the pill has to
  // stay on screen or there is no way to switch it back on.
  var MIN_LANE_H=56;
  // Mix a hex colour toward white (tint) or toward black (shade). Used to build
  // each pill's off-state fill and text colour from its sector colour, so the
  // five palette entries in SEC stay the single source of truth.
  function mix(hex,amt,toward){
    var r=parseInt(hex.substr(1,2),16),g=parseInt(hex.substr(3,2),16),b=parseInt(hex.substr(5,2),16);
    r=Math.round(r+(toward-r)*amt); g=Math.round(g+(toward-g)*amt); b=Math.round(b+(toward-b)*amt);
    return "rgb("+r+","+g+","+b+")";
  }
  function tint(hex,amt){return mix(hex,amt,255);}
  function shade(hex,amt){return mix(hex,amt,0);}
  // Everything that makes a legend entry look like a pill. This used to live in
  // §24 of styles.css. It sits here now because the three colours already had
  // to be computed in this file from SEC, and splitting one control's
  // appearance across two files means neither is the source of truth. The
  // per-pill values (position, size, the three colours) are merged over this
  // base where each pill is built.
  var PILL={
    position:"absolute",
    height:"52px",                  // identical for all five, so the one-line
                                    // names centre in the same box as the
                                    // two-line ones instead of shrinking
    display:"flex",
    alignItems:"center",            // centres one or two lines vertically
    justifyContent:"center",        // centres the line box horizontally
    textAlign:"center",             // centres the second line under the first
    boxSizing:"border-box",         // width below is the outer width
    padding:"6px 14px",
    borderStyle:"solid",
    borderWidth:"1.5px",
    borderRadius:"999px",           // capsule ends; on a wrapped label this
                                    // reads as a lozenge, which is intended
    fontSize:"13px",
    fontWeight:"600",
    lineHeight:"1.25",
    transform:"translateY(-50%)",   // the pill is positioned at its lane's
                                    // midpoint and this centres it there
    cursor:"pointer",
    userSelect:"none",              // a fast double click toggles twice rather
    WebkitUserSelect:"none",        // than selecting the label text
    transition:"background .15s ease, color .15s ease, box-shadow .15s ease"
  };
  var wrap=document.querySelector(".jtl-wrap"); if(!wrap) return;
  var chart=wrap.querySelector(".jtl-chart");
  var tip=document.createElement("div"); tip.className="jtl-tip"; wrap.appendChild(tip);
  // ── Measuring, packing, and label placement ─────────────────────────────
  // A bar carries its name inside it when the bar is wide enough and beside it
  // when it is not. The previous version decided that one bar at a time, after
  // the rows had already been packed, by comparing the name against the raw
  // distance to the neighbouring bar. When neither side had room it picked the
  // larger of the two gaps and drew the name there anyway. That is how
  // "Ecological Modeling Course" came to sit on top of the Greensboro Science
  // Center bar: both gaps were too small, and the one to its left was the
  // bigger of the two.
  //
  // The three functions below replace that. Names are measured first, the
  // packer is told to reserve the room an outside name will need, and the two
  // run as a short loop: pack, place the names, and if a name still has
  // nowhere to sit, reserve room for it and pack again. A bar drops to a new
  // row only when it genuinely cannot share one, so rows that already read
  // well are left alone. Santa Barbara Coastal Long Term Ecological Research
  // with its name to the left and Caselle Lab with its name to the right stay
  // exactly where they are.
  var OUT_GAP=7,                    // matches margin-left and margin-right on
                                    // .jtl-out and .jtl-out-left in §24 of
                                    // styles.css
      OUT_CLEAR=12,                 // clear space demanded between an outside
                                    // name and whatever lies beyond it, so the
                                    // two never touch
      IN_PAD=18;                    // the 9px of padding on each side of
                                    // .jtl-in, which is what an inside name
                                    // needs on top of the text itself

  // Every name measured once per draw, in the same font the outside labels
  // use, against a hidden span inside the chart so it inherits that font. The
  // width goes on the item as _tw and everything downstream reads it from
  // there, which is what lets the packer know about a name before the bar
  // carrying it exists.
  function measure(){
    var m=document.createElement("span");
    m.className="jtl-out";
    m.style.position="absolute";    // .jtl-out is positioned against its bar,
    m.style.left="0";               // and there is no bar yet, so the three
    m.style.margin="0";             // positioning declarations are overridden
    m.style.visibility="hidden";
    chart.appendChild(m);
    // Two pixels on top of the measurement. A browser lays text out on
    // fractional pixels and rounds when it paints, so a name can render a
    // shade wider than it measured, which is enough to close a gap that the
    // arithmetic thought it had.
    E.forEach(function(it){ m.textContent=it[1]; it._tw=Math.ceil(m.getBoundingClientRect().width)+2; });
    chart.removeChild(m);
  }

  // One-off measurement for text that is not a bar name, in whatever class
  // will end up carrying it. Same hidden-span trick as measure() above.
  function textw(str,cls){
    var m=document.createElement("span");
    m.className=cls;
    m.style.position="absolute"; m.style.left="0"; m.style.top="0";
    m.style.margin="0"; m.style.visibility="hidden"; m.style.whiteSpace="nowrap";
    chart.appendChild(m);
    m.textContent=str;
    var w=Math.ceil(m.getBoundingClientRect().width);
    chart.removeChild(m);
    return w;
  }

  // Rows are packed on pixel extents rather than on years, because a name is
  // measured in pixels and the whole point is to pack around it. An item with
  // _res set has claimed room for an outside name on that side, and that room
  // is part of its extent.
  function pack(items,x){
    var s=items.slice().sort(function(a,b){return a[4]-b[4];});
    var rows=[];
    for(var i=0;i<s.length;i++){
      var it=s[i];
      var L=x(it[4])-(it._res===2?OUT_GAP+it._tw:0);
      var R=x(it[5])+(it._res===1?OUT_GAP+it._tw:0);
      var placed=false;
      for(var r=0;r<rows.length;r++){
        if(rows[r]<=L+0.5){        // half a pixel of tolerance, so two bars
                                    // that meet exactly, as the Long Term
                                    // Ecological Research and Caselle Lab
                                    // entries do, still share a row
          it._row=r; rows[r]=R; placed=true; break;
        }
      }
      if(!placed){ it._row=rows.length; rows.push(R); }
    }
    return {items:s,n:rows.length};
  }

  // Walks each row left to right and gives every name a home: 0 inside the
  // bar, 1 to its right, 2 to its left. Returns true if any item had to claim
  // reserved room, which tells render() to pack once more.
  function placeLabels(lane,x,W,nx){
    // A name may not straddle the vertical "now" rule. Before this, two of
    // them did: the rule ran through the word "Media" in Environmental Media
    // Production and through "Mitigation" in Mitigation Monitoring Program.
    // Bars are allowed to cross it, because a job that is still running should
    // read as still running; it is only the text that has to keep clear.
    function hitsNow(a,b){ return a<nx+NOW_CLEAR && b>nx-NOW_CLEAR; }
    var changed=false, byRow={};
    lane.items.forEach(function(it){ (byRow[it._row]=byRow[it._row]||[]).push(it); });
    Object.keys(byRow).forEach(function(r){
      var arr=byRow[r].sort(function(a,b){return a[4]-b[4];});
      var occ=LABEL_W;              // right edge of everything already placed
                                    // on this row, names included; the track
                                    // starts at LABEL_W so nothing sits before
      for(var i=0;i<arr.length;i++){
        var it=arr[i], bl=x(it[4]), br=x(it[5]);
        if(it._tw+IN_PAD<=br-bl){ it._side=0; occ=br; continue; }
        var need=it._tw+OUT_GAP+OUT_CLEAR;
        var nextL=(i+1<arr.length)?x(arr[i+1][4]):W;
        // Whether a side is usable at all, before asking whether the gap on
        // that side is wide enough: the name has to stay inside the chart, or
        // right of the legend gutter, and clear of the "now" rule.
        var okR=(br+OUT_GAP+it._tw<=W)&&!hitsNow(br+OUT_GAP,br+OUT_GAP+it._tw);
        var okL=(bl-OUT_GAP-it._tw>=LABEL_W)&&!hitsNow(bl-OUT_GAP-it._tw,bl-OUT_GAP);
        var fitR=okR&&(nextL-br>=need);
        var fitL=okL&&(bl-occ>=need);
        // An item that already claimed a side keeps it, so the loop in
        // render() settles instead of swinging the same name back and forth.
        var first=(it._res===2)?2:1;
        var got=0;
        if(first===1){ got=fitR?1:(fitL?2:0); } else { got=fitL?2:(fitR?1:0); }
        if(got===0){
          // Neither side has room on this row. Claim the wider of the two and
          // let the next pack push whatever is in the way down a row.
          // Prefer a usable side over an unusable one, and only then the side
          // with more room. A name that has to go somewhere still goes to the
          // side that keeps it off the rule.
          got=(okL&&(!okR||bl-occ>=nextL-br))?2:1;
          if(it._res===0){ it._res=got; changed=true; }
        }
        it._side=got;
        occ=(got===1)?br+OUT_GAP+it._tw:br;
      }
    });
    return changed;
  }
  function render(){
    var W=chart.clientWidth; if(W<40) return; chart.innerHTML="";
    var trackW=Math.max(280,W-LABEL_W-RIGHT_PAD);
    var x=function(y){return LABEL_W+((y-T0)/(T1-T0))*trackW;};
    var nx=x(NOW);                  // needed by the packing loop below as well
                                    // as by the "now" pill further down
    measure();
    // Reservations are cleared at the top of every draw rather than carried
    // over, so a window that gets wider goes back to the compact arrangement
    // instead of keeping rows it needed at a narrower size.
    E.forEach(function(it){ it._res=0; });
    var lanes;
    for(var pass=0;pass<4;pass++){
      lanes=ORDER.map(function(k){var p=pack(ACTIVE[k]?E.filter(function(e){return e[0]===k;}):[],x);p.key=k;return p;});
      var changed=false;
      lanes.forEach(function(l){ if(placeLabels(l,x,W,nx)) changed=true; });
      if(!changed) break;
                                    // Four passes is a ceiling, not a target.
                                    // Each item can claim room only once per
                                    // draw, so the loop settles after one or
                                    // two rounds; the cap is there to make a
                                    // runaway impossible rather than because
                                    // it is expected to be reached.
    }
    // A switched-off lane packs to zero rows, and n*ROW_H+(n-1)*ROW_GAP would
    // then be -5, so its natural height is clamped at zero before the floor is
    // applied. _rowOff then re-centres the bars inside a lane that the floor
    // made taller than its rows need, so bars and pill stay on the same line.
    var y=LANES_TOP; lanes.forEach(function(l){
      var rowsH=ACTIVE[l.key]?Math.max(0,l.n*ROW_H+(l.n-1)*ROW_GAP):0;
      l._top=y; l._h=Math.max(MIN_LANE_H,rowsH); l._rowOff=(l._h-rowsH)/2;
      y+=l._h+LANE_GAP;
    });
    var lb=y-LANE_GAP, axisTop=lb+10; chart.style.height=(axisTop+AXIS_H+CAP_H)+"px";
    function el(c,s,t){var d=document.createElement("div");d.className=c;if(s)Object.assign(d.style,s);if(t!=null)d.textContent=t;chart.appendChild(d);return d;}

    // Draws a vertical rule from top to bot at px, in as many pieces as it
    // takes to avoid every box handed to it. A box is any run of text the rule
    // would otherwise cross: a milestone caption, or a bar name that had
    // nowhere else to go. A reference line interrupted where it meets a label
    // still reads as one line, which is the convention a printed map uses for
    // a gridline crossing a place name.
    function vrule(cls,px,top,bot,boxes){
      var gaps=[];
      boxes.forEach(function(b){
        if(px>b.l-NOW_CLEAR && px<b.r+NOW_CLEAR){ gaps.push([b.t-3,b.b+3]); }
      });
      gaps.sort(function(p,q){return p[0]-q[0];});
      var segTop=top;
      gaps.forEach(function(g){
        if(g[0]>segTop){ el(cls,{left:px+"px",top:segTop+"px",height:(g[0]-segTop)+"px"}); }
        segTop=Math.max(segTop,g[1]);
                                    // max rather than assignment, so two boxes
                                    // that overlap produce one break instead
                                    // of a negative-height segment
      });
      if(bot>segTop){ el(cls,{left:px+"px",top:segTop+"px",height:(bot-segTop)+"px"}); }
    }
    var uL=x(2021.67),uR=x(2025.42);
    el("jtl-band jtl-band-ug",{left:uL+"px",top:RIBBON_H+"px",width:(uR-uL)+"px",height:(lb-RIBBON_H)+"px"});
    var fL=x(NOW),fR=x(T1); el("jtl-band jtl-band-fu",{left:fL+"px",top:RIBBON_H+"px",width:(fR-fL)+"px",height:(lb-RIBBON_H)+"px"});
    for(var yr=2019;yr<=2027;yr++){el("jtl-gl",{left:x(yr)+"px",top:RIBBON_H+"px",height:(lb-RIBBON_H)+"px"});}
    var baseY=RIBBON_H-12;

    // ── Milestones ─────────────────────────────────────────────────────────
    // Captions are drawn first and their boxes recorded, then the stems are
    // drawn around them. A stem that starts at the top level has to fall past
    // the two levels below it, and if a caption is sitting there it used to
    // run straight through the words: the First Publications stem crossed
    // "Finished Undergraduate Degree (UCSB)" one level down. The stem now
    // breaks around any caption in its path, the same way the "now" rule
    // breaks around a bar name.
    //
    // A caption is centred on its date by a CSS transform and capped at 150px,
    // so its box is measured from the rendered element rather than assumed:
    // a long caption wraps to two lines and is taller than a short one.
    var msBox=MS.map(function(m){
      var mx=x(m[0]),ly=msTop(m[2]);
      var lab=el("jtl-mslabel",{left:mx+"px",top:ly+"px",maxWidth:"150px"},m[1]);
      if(m[3])lab.style.color="#8A5E12";
      var r=lab.getBoundingClientRect();
      return {l:mx-r.width/2, r:mx+r.width/2, t:ly, b:ly+r.height};
    });
    MS.forEach(function(m,i){
      // The stem starts below its own caption. The old fixed 30px assumed a
      // caption of at most two lines; a long one at a large text size runs to
      // three, and the stem then began inside its own words. Measured bottom
      // plus a little air, floored at the old value so short captions look
      // exactly as they did.
      var mx=x(m[0]),st=Math.max(msTop(m[2])+30,msBox[i].b+8);
      vrule("jtl-stem",mx,st,Math.max(st+2,baseY),msBox.filter(function(b,j){return j!==i;}));
      if(m[3]){el("jtl-star",{left:mx+"px",top:baseY+"px"},"★");}
      else{el("jtl-msdot",{left:mx+"px",top:baseY+"px"});}
    });
    if(FUT){ el("jtl-fut",{left:x(FUT[0])+"px",top:msTop(2)+"px"},FUT[1]+" \u2197"); }
    // The "now" pill used to sit at the top of the lane area, where it landed
    // on top of whatever bar happened to be running. It now sits up in the
    // milestone caption band, on the same line as a milestone label, with its
    // rule starting underneath it. Pick the lowest of the three caption levels
    // that has no milestone label within 95px, so the pill never collides with
    // one at a narrow window width.
    var nlv=1;                      // nx was computed at the top of render()
    for(var lv=1;lv<=3;lv++){
      var clash=false;
      for(var mi=0;mi<MS.length;mi++){ if(MS[mi][2]===lv && Math.abs(x(MS[mi][0])-nx)<95){clash=true;break;} }
      if(!clash){nlv=lv;break;}
    }
    var ntop=msTop(nlv);
    el("jtl-nowtag",{left:nx+"px",top:ntop+"px"},"now");

    // ── The "now" rule ─────────────────────────────────────────────────────
    // placeLabels keeps bar names off the rule wherever it can, but at a
    // cramped window width a name can end up with no usable side: too long to
    // fit between its bar and the legend gutter on the left, and crossing the
    // rule on the right. Those names, and any milestone caption in the way,
    // become boxes the rule breaks around.
    var boxes=msBox.slice();
    lanes.forEach(function(l){
      l.items.forEach(function(it){
        if(it._side===0) return;    // a name inside its bar is never on a rule
        var bl=x(it[4]),br=x(it[5]);
        var t=l._top+l._rowOff+it._row*(ROW_H+ROW_GAP);
        boxes.push({
          l:(it._side===1)?br+OUT_GAP:bl-OUT_GAP-it._tw,
          r:(it._side===1)?br+OUT_GAP+it._tw:bl-OUT_GAP,
          t:t, b:t+ROW_H
        });
      });
    });
    vrule("jtl-now",nx,ntop+26,lb,boxes);
    lanes.forEach(function(l){
      var sec=SEC[l.key];
      // The lane label doubles as the legend and as the filter control for its
      // sector. Vertical centring is now done by a CSS transform rather than by
      // subtracting half a guessed label height, because the label is taller
      // than it was and wraps to two lines for the longer sector names.
      var off=!ACTIVE[l.key];
      // The pill carries its sector colour itself, so the separate square
      // swatch that used to sit beside the text is gone. On means a solid fill
      // in the sector colour with white text; off means a pale tint of the same
      // colour with a dark shade of it for text. The border is the sector
      // colour in both states, which is what keeps an off pill legible as
      // belonging to that sector rather than just looking greyed out.
      // left and width are set here rather than in the stylesheet because both
      // derive from LABEL_W, and a gutter width and the thing centred inside it
      // should not be defined two files apart. PILL_M is the margin on each
      // side, so all five pills are identical in size and share one axis.
      var lab=el("jtl-lane"+(off?" jtl-off":""),Object.assign({},PILL,{
        top:(l._top+l._h/2)+"px",
        left:PILL_M+"px",
        width:(LABEL_W-2*PILL_M)+"px",
        borderColor:sec[1],
        background:off?tint(sec[1],.88):sec[1],
        color:off?shade(sec[1],.40):"#fff",
        fontWeight:off?"500":"600"
      }),sec[0]);
      // Hover and focus are handled here rather than by :hover and
      // :focus-visible, for the same single-source reason as PILL above.
      lab.addEventListener("mouseenter",function(){lab.style.boxShadow="0 3px 10px rgba(20,32,42,.18)";});
      lab.addEventListener("mouseleave",function(){lab.style.boxShadow="";});
      lab.addEventListener("focus",function(){lab.style.outline="2px solid #D1796B";lab.style.outlineOffset="3px";});
      lab.addEventListener("blur",function(){lab.style.outline="";});
      lab.setAttribute("role","button");
      lab.setAttribute("tabindex","0");
      lab.setAttribute("aria-pressed",off?"false":"true");
      lab.setAttribute("aria-label",(off?"Show ":"Hide ")+sec[0]);
      var toggle=function(){ACTIVE[l.key]=!ACTIVE[l.key];render();};
      lab.addEventListener("click",toggle);
      // Enter and Space are what a real <button> responds to; this is a div
      // carrying role="button", so the behaviour has to be supplied by hand.
      lab.addEventListener("keydown",function(ev){if(ev.key==="Enter"||ev.key===" "){ev.preventDefault();toggle();}});
      l.items.forEach(function(it){
        var left=x(it[4]),w=Math.max(7,x(it[5])-left);
        var bar=document.createElement("div");bar.className="jtl-bar"+(it[7]?" jtl-cur":"");
        Object.assign(bar.style,{left:left+"px",top:(l._top+l._rowOff+it._row*(ROW_H+ROW_GAP))+"px",width:w+"px",background:sec[1]});
        chart.appendChild(bar);
        // _side was settled by placeLabels above, so nothing is decided here.
        if(it._side===0){
          var inr=document.createElement("span");inr.className="jtl-in";inr.textContent=it[1];bar.appendChild(inr);
        }else{
          var o=document.createElement("span");o.textContent=it[1];
          o.className=(it._side===2)?"jtl-out-left":"jtl-out";
          bar.appendChild(o);
        }
        bar.addEventListener("mouseenter",function(){tip.innerHTML="<b>"+it[2]+"</b>"+it[3]+"<br><i>"+it[6]+"</i>";tip.style.opacity="1";var bx=bar.offsetLeft,by=bar.offsetTop+chart.offsetTop;tip.style.left=Math.max(0,Math.min(bx,wrap.clientWidth-250))+"px";tip.style.top=(by-tip.offsetHeight-8)+"px";});
        bar.addEventListener("mouseleave",function(){tip.style.opacity="0";});
      });
    });
    for(var t=2018;t<=2027;t++){el("jtl-tick",{left:x(t)+"px",top:axisTop+"px"},t);}

    // ── The undergraduate caption ──────────────────────────────────────────
    // This used to sit inside the shaded band, along its bottom edge, where
    // the gridlines and the bottom lane of bars ran through it. It is a
    // caption for the band rather than an object inside the chart, so it now
    // sits below the year axis: a short bracket spanning the same years, and
    // the words centred under it.
    //
    // Both pieces are styled inline rather than from §24 of styles.css. The
    // bracket is a shape that exists only here and has no other user, and the
    // caption only needs two declarations on top of .jtl-blabel, so adding
    // two class names to the stylesheet would mean opening two files to move
    // one caption.
    var capY=axisTop+AXIS_H;
    el("",{position:"absolute",left:uL+"px",top:capY+"px",width:(uR-uL)+"px",height:"2px",borderRadius:"2px",background:"rgba(62,110,134,.35)"});
    // Centred on the band, then pulled back inside the chart if the band is
    // narrow enough at this width that centring would push the words past
    // either edge. transform does the centring, so the clamp works on the
    // centre point rather than on the left edge.
    var capW=textw("University of California, Santa Barbara","jtl-blabel");
    var capX=Math.min(Math.max((uL+uR)/2,LABEL_W+capW/2),W-capW/2);
    el("jtl-blabel",{left:capX+"px",top:(capY+8)+"px",transform:"translateX(-50%)"},"University of California, Santa Barbara");
  }
  render();
  // Everything above is measured, and on a cold load the first measurement can
  // happen while Inter is still downloading, against whatever fallback face the
  // browser is showing. Text then reflows a shade wider when the real font
  // lands, which is enough to close a gap the arithmetic thought it had. One
  // redraw once the fonts report ready fixes that, and costs nothing on a warm
  // load because the promise is already settled.
  if(document.fonts&&document.fonts.ready){ document.fonts.ready.then(render); }
  if(window.ResizeObserver){var last=0;new ResizeObserver(function(){var w=chart.clientWidth;if(Math.abs(w-last)>4){last=w;render();}}).observe(chart);}
  window.addEventListener("resize",render);
})();
</script>

  </div>
</div>

<!-- ========= COURSEWORK ========= -->
<div class="section-band" id="coursework">
  <div class="band-inner">

## Coursework

```{r, echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}

cw <- read.csv("data/coursework.csv", stringsAsFactors = FALSE,
               na.strings = c("NA", ""), fileEncoding = "UTF-8-BOM")

# An academic year runs fall to summer, so a winter, spring or summer term
# belongs to the year that began the previous fall. Without this, Fall 2021 and
# Spring 2022 would land in different rows despite being one year of study.
# as.integer matters: ifelse can return a double here, and sprintf("%d", ...)
# rejects doubles outright rather than rounding them.
cw$ay <- as.integer(ifelse(cw$season == "Fall", cw$year, cw$year - 1L))

SEASONS <- c("Fall", "Winter", "Spring", "Summer")

# One color per subject area. The palette lives here rather than in the
# stylesheet because the area names come out of the CSV, and a second copy of
# that list in section 29 would drift. Every value of the area column needs a
# key: a missing one is a subscript-out-of-bounds error at render, not a
# missing color at display.
pal <- c("marine and ecology"       = "#3E6E86",
         "independent research"     = "#D1796B",
         "quantitative and spatial" = "#6D6A9C",
         "chemistry and molecular"  = "#5E8D7E",
         "study abroad"             = "#C08A3E",
         "general education"        = "#8C8C86",
         "advanced placement"       = "#7A8B99")

stopifnot(all(cw$area %in% names(pal)))   # Fail loudly here rather than 80%
                                          # through the render with a backtrace.

esc <- function(x) {
  x <- gsub("&", "&amp;", x, fixed = TRUE); x <- gsub("<", "&lt;", x, fixed = TRUE)
  x <- gsub(">", "&gt;", x, fixed = TRUE);  x <- gsub('"', "&quot;", x, fixed = TRUE)
  gsub("'", "&#39;", x, fixed = TRUE)
}
slug <- function(x) gsub("[^a-z0-9]+", "-", tolower(x))

# Mix a hex colour toward white, for the tinted chip fills. strtoi, not strtoint.
tint <- function(hex, amt) {
  r <- strtoi(substr(hex, 2, 3), 16L)
  g <- strtoi(substr(hex, 4, 5), 16L)
  b <- strtoi(substr(hex, 6, 7), 16L)
  sprintf("rgb(%d,%d,%d)", round(r + (255 - r) * amt),
                           round(g + (255 - g) * amt),
                           round(b + (255 - b) * amt))
}

is_ap <- cw$area == "advanced placement"

# UCSB accepted 48 quarter units for the Advanced Placement exams, recorded on
# the transcript as one transfer block covering Spring 2019 to Spring 2020 with
# no per-exam split. The AP rows in the CSV therefore carry zero units, and the
# figure lives here as the one number the transcript actually states. Splitting
# 48 across ten classes would mean inventing a breakdown that does not exist.
AP_UNITS <- 48

# ── Headline numbers ──────────────────────────────────────────────────────────
# Advanced Placement is held apart from the course count and the unit total.
# Those are high school classes, and folding them in would inflate both figures
# and stop them matching the transcript.
o <- character(0)
o <- c(o, '<p class="cw-summary">',
  sprintf('<span><strong>%d</strong> undergraduate courses</span>', sum(!is_ap)),
  sprintf('<span><strong>%s</strong> units, plus <strong>%d</strong> accepted from Advanced Placement</span>',
          format(sum(cw$units[!is_ap])), AP_UNITS),
  sprintf('<span><strong>%d</strong> graduate courses (taken as an undergraduate)</span>',
          sum(cw$level == "graduate")),
  sprintf('<span><strong>%d</strong> quarters of independent research</span>',
          sum(cw$area == "independent research")),
  '</p>')

# ── Controls ──────────────────────────────────────────────────────────────────
o <- c(o, '<div class="cw-filters">')
for (a in names(pal)) {
  n <- sum(cw$area == a); if (n == 0) next
  o <- c(o, sprintf(paste0('<button type="button" class="cw-pill is-on" ',
      'data-area="%s" style="--c:%s;--t:%s" aria-pressed="true">%s ',
      '<span class="cw-count">%d</span></button>'),
      slug(a), pal[[a]], tint(pal[[a]], .88), esc(a), n))
}
o <- c(o, paste0('<button type="button" class="cw-expand" ',
                 'aria-expanded="false">Expand All</button>'))
o <- c(o, '</div>')

# ── The calendar ──────────────────────────────────────────────────────────────
# Each academic year is its own grid row element rather than one grid spanning
# the whole table. Every row shares the same column template so columns still
# line up, and hiding a year when a filter empties it is then one element
# rather than five. Every line is flush left: four leading spaces inside a raw
# HTML block is an indented code block to pandoc, which would render the whole
# calendar as a grey code box.
o <- c(o, '<div class="cw-grid">')
o <- c(o, '<div class="cw-row cw-head">', '<div class="cw-yr"></div>')
for (s in SEASONS) o <- c(o, sprintf('<div class="cw-colhead">%s</div>', s))
o <- c(o, '</div>')

# Running total of UC units, carried across the whole loop rather than reset per
# year, so the figure under each year label is units to date. The AP rows add
# nothing to it, which is correct: that credit transferred in as a block. It
# also ignores the subject filters, because a total that moved when you clicked
# a pill would be reporting something else.
cum <- 0

for (y in sort(unique(cw$ay))) {
  cum <- cum + sum(cw$units[cw$ay == y])
  o <- c(o, '<div class="cw-row">', '<div class="cw-yr">',
            sprintf('<span class="cw-yr-label">%d-%d</span>', y, y + 1L),
            sprintf('<span class="cw-yr-cum">%s units</span>', format(cum)),
            '</div>')
  for (s in SEASONS) {
    rows <- cw[cw$ay == y & cw$season == s, ]

    if (nrow(rows) == 0) {
      o <- c(o, '<div class="cw-cell cw-none">',
                '<span class="cw-empty" aria-hidden="true"></span>', '</div>')
      next
    }

    # Collapsed view: one bar per course, in the order taken. The bars carry the
    # same cw-<area> class as the chips so one filter rule reaches both.
    bars <- character(0)
    for (i in seq_len(nrow(rows))) {
      r <- rows[i, ]
      bars <- c(bars, sprintf(
        '<span class="cw-bar cw-%s" style="--c:%s"></span>',
        slug(r$area), pal[[r$area]]))
    }

    # A quarter of AP classes has no UC units to tally, and "0 units" under it
    # would read as a failure rather than as credit recorded elsewhere.
    qu <- sum(rows$units)

    # The grid item is a div wrapping the <details>, not the <details> itself.
    # Chrome will not stretch a <details> grid item: measured on the page, four
    # details cells sat at 119.88px inside a 137.875px track while the div cells
    # beside them filled it. So the empty quarters, which are divs, stood taller
    # than the full ones no matter what set the track. A div outside and the
    # details inside makes every cell in the row the same kind of box.
    o <- c(o, '<div class="cw-cell">', '<details class="cw-inner">',
      '<summary class="cw-sum">',
      sprintf('<span class="cw-bars">%s</span>', paste(bars, collapse = "")),
      sprintf('<span class="cw-qtotal">%s</span>',
              if (qu > 0) paste(format(qu), "units") else "AP Year"),
      '</summary>', '<div class="cw-open">')

    for (i in seq_len(nrow(rows))) {
      r <- rows[i, ]
      grad <- if (r$level == "graduate") " cw-grad" else ""
      note <- if (!is.na(r$note) && nzchar(r$note))
                sprintf('<span class="cw-note">%s</span>', esc(r$note)) else ""
      o <- c(o, sprintf(paste0('<span class="cw-course cw-%s%s" ',
          'style="--c:%s;--t:%s" title="%s units"><span class="cw-code">%s</span>',
          '<span class="cw-title">%s</span>%s</span>'),
          slug(r$area), grad, pal[[r$area]], tint(pal[[r$area]], .9),
          esc(r$units), esc(r$code), esc(r$title), note))
    }
    o <- c(o, '</div>', '</details>', '</div>')
  }
  o <- c(o, '</div>')
}
o <- c(o, '</div>')

cat('<div class="cw">\n'); cat(paste(o, collapse = "\n")); cat('\n</div>\n')
```

<p class="cw-key">Each bar is one course, coloured by subject. Hollow bars are Advanced Placement, which transferred in as credit rather than being taken at the university. Click a quarter to open it. A ring on a course marks graduate level.</p>

<script>
/* Subject filter and expand-all. Inline rather than in scripts/site.js for the
   same reason the timeline's script is: this is one page's widget, and site.js
   is for behaviour that repeats across the site. Opening and closing a quarter
   needs no script at all; <details> does that natively. */
(function () {
  var root = document.querySelector('#coursework .cw');
  if (!root) return;

  function refresh() {
    /* A quarter with nothing left after filtering goes VACANT rather than
       hidden: the cell keeps its place in the grid and renders as the empty
       teal block, the same as a quarter that never had any courses in it.

       This used to set d.hidden, which takes the cell out of the grid
       altogether, and every quarter after it in that year then slid one column
       to the left. Switching off study abroad emptied Fall 2023-2024 and moved
       Winter's courses into the Fall column, which is a worse outcome than the
       blank cell the hiding was meant to avoid. A calendar's columns have to
       keep meaning what they say. */
    root.querySelectorAll('details.cw-inner').forEach(function (d) {
      var any = Array.prototype.some.call(
        d.querySelectorAll('.cw-course'), function (c) { return !c.hidden; });
      d.classList.toggle('cw-vacant', !any);
      d.setAttribute('aria-hidden', any ? 'false' : 'true');
    });
    /* A year with no quarters left still hides outright. Each year is its own
       grid, so removing a whole row cannot shift anything sideways. */
    root.querySelectorAll('.cw-row:not(.cw-head)').forEach(function (r) {
      var any = Array.prototype.some.call(
        r.querySelectorAll('details.cw-inner'),
        function (d) { return !d.classList.contains('cw-vacant'); });
      r.hidden = !any;
    });
  }

  root.querySelectorAll('.cw-pill').forEach(function (p) {
    p.addEventListener('click', function () {
      var on = p.classList.toggle('is-on');
      p.setAttribute('aria-pressed', on ? 'true' : 'false');
      /* Hides the chip and its bar in one pass: both carry cw-<area>. */
      root.querySelectorAll('.cw-' + p.dataset.area).forEach(function (el) {
        if (el.classList.contains('cw-course') || el.classList.contains('cw-bar')) {
          el.hidden = !on;
        }
      });
      refresh();
    });
  });

  var expand = root.querySelector('.cw-expand');
  if (expand) {
    expand.addEventListener('click', function () {
      var open = expand.getAttribute('aria-expanded') !== 'true';
      root.querySelectorAll('details.cw-inner').forEach(function (d) {
        d.open = open;
      });
      expand.setAttribute('aria-expanded', open ? 'true' : 'false');
      expand.textContent = open ? 'Collapse all' : 'Expand All';
    });
  }
})();
</script>

  </div>
</div>

<!-- ========= PERSONAL ========= -->
<div class="section-band" id="personal">
  <div class="band-inner">

## Personal

::: {.stacked-cards}

::: {.card}
### Photography
<div class="metrics">
  <span class="pill">Underwater</span>
  <span class="pill">Microscopy</span>
  <span class="pill">Coast and Portraits</span>
</div>

Most of my photography happens either on a dive or down a microscope. The range is wider than it sounds: the same interest in structure that makes a kelp canopy worth shooting is what makes a copepod worth shooting, just at a different working distance.

<details class="details-panel" markdown="1">
<summary>More on Photography</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
**Underwater:** kelp forest canopies, reef structure, and the animals that hold still long enough on a low-visibility dive.  
</div>

<div class="detail-block" markdown="1">
**Microscopy:** copepods, parasites, and the fine anatomy behind the figures in my papers. Several of these started as working images and turned out to be worth printing.  
</div>

<div class="detail-block" markdown="1">
**Above water:** coastlines, working harbors, and portraits of the people doing the work.  
</div>

<div class="detail-block" markdown="1">
[See Photography →](photography.html)
</div>

</div><!-- /.detail-stack -->
</details>
:::

::: {.card}
### Painting
<div class="metrics">
  <span class="pill">Wildlife Portraits</span>
  <span class="pill">Coastal Landscapes</span>
  <span class="pill">Mixed Media</span>
</div>

I paint in oil and mixed media, mostly places I have been in the water and animals I have spent time around. It is the only part of my practice with no data in it, which is most of the appeal.

<details class="details-panel" markdown="1">
<summary>More on Painting</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
**Subjects:** coastal bays, trout streams, places I know well, and animals with a story attached, sometimes literal and sometimes not.  
</div>

<div class="detail-block" markdown="1">
**How it works:** some paintings are observational and some are assembled from field impressions months after the fact. The assembled ones usually turn out better.  
</div>

<div class="detail-block" markdown="1">
**Why it matters:** painting is slow in a way that fieldwork and code are not, and it is where I actually learned how light, pattern, and atmosphere behave. That reading carries straight into figure design.  
</div>

<div class="detail-block" markdown="1">
[See Art →](art.html)
</div>

</div>
</details>
:::

::: {.card}
### Trails, Diving, and Travel
<div class="metrics">
  <span class="pill">Coastal Hikes</span>
  <span class="pill">Night and Low Visibility</span>
  <span class="pill">Working Harbors</span>
</div>

Most weekends I’m on a coastal trail or underwater, and travel tends to follow coastlines and working harbors rather than cities.

<details class="details-panel" markdown="1">
<summary>More on Trails and Travel</summary>

<div class="detail-stack">

<div class="detail-block" markdown="1">
**Hiking:** coastal bluffs, estuary loops, and any trail that ends at a tidepool. A pocket notebook usually comes along for sketches.  
</div>

<div class="detail-block" markdown="1">
**Diving:** roughly three quarters of my logged dives are recreational rather than scientific, and the habits transfer in both directions. Kelp holdfasts, night entries, and low-visibility marsh work all reward the same discipline.  
</div>

<div class="detail-block" markdown="1">
**Travel:** I gravitate to places where ecology, fisheries, and community sit close together. It is good preparation for the conversations that fisheries work eventually turns into.  
</div>

</div>
</details>
:::
:::

  </div>
</div>

<!-- ========= HONORS & AWARDS ========= -->
<div class="coral-banner" markdown="1">

## Honors and Awards

**Degree** • Bachelor of Arts in Biology with High Honors, College of Creative Studies, University of California, Santa Barbara

**Scholarships and Grants** • Regents Scholar, University of California, Santa Barbara • Coastal Fund Major Grants

**Conference Awards** • Best Student Presentation, International Conference on Copepoda • Best Student Poster, Southern Academy of Parasitologists • Honorable Mention, Western Society of Naturalists
</div>

<div class="gallery-footer">
  <a class="read-more" href="#">Back to Top</a>
  <a class="btn btn-primary" href="contact.html">Contact</a>
</div>
