---
title: ""
pagetitle: "Terrestrial Photography"
format:
  html:
    page-layout: full
    toc: false
execute:
  echo: false
  warning: false
  message: false
---

<div class="page-banner" role="img" aria-label="Terrestrial Photography banner">
<video
autoplay muted loop playsinline
class="page-banner-video">
<source src="videos/terrestrial.mp4" type="video/mp4">
</video>

<div class="page-banner-overlay"></div>

<div class="page-banner-inner" markdown="1">
  
# Terrestrial Photography {.page-banner-title}
<p class="page-banner-subtitle">desert light • coastline edges • quiet transitions</p>

  </div>
</div>

```{r setup-utf8, include=FALSE}
try(Sys.setlocale("LC_CTYPE", "en_US.UTF-8"), silent = TRUE)
options(encoding = "UTF-8")

knitr::knit_hooks$set(output = function(x, options) {
  Encoding(x) <- "UTF-8"
  enc2utf8(x)
})
```

```{r, results='asis'}
library(here)
library(tidyverse)
library(fs)
library(glue)

source("scripts/render_gallery.R")
```


```{r, results='asis'}
render_gallery(
  category      = "terrestrial",
  metadata_file = "data/terrestrial_metadata.csv",
  path_prefix   = "images"
)
```

<div class="gallery-footer">
  <a class="btn btn-primary" href="photography.html">Back to Photography</a>
  <a class="read-more" href="#">Back to top</a>
</div>

<!-- Lightweight client-side randomizer.
     Shuffles each .masonry gallery on page load so you don't
     have to rebuild large shuffled HTML. Set MODE to 'daily'
     to keep a stable order per day. -->
<script>
  (function () {
    function mulberry32(a) {
      return function () {
        var t = a += 0x6D2B79F5;
        t = Math.imul(t ^ (t >>> 15), t | 1);
        t ^= t + Math.imul(t ^ (t >>> 7), t | 61);
        return ((t ^ (t >>> 14)) >>> 0) / 4294967296;
      };
    }

  const MODE = 'always'; // 'always' | 'daily'

  function shuffleNodes(container, mode) {
    const items = Array.from(container.children);
    if (items.length < 2) return;

  let rand = Math.random;
    if (mode === 'daily') {
        const day = new Date().toISOString().slice(0, 10); // YYYY-MM-DD
        let seed = 2166136261;
        for (let i = 0; i < day.length; i++) {
          seed ^= day.charCodeAt(i);
          seed = Math.imul(seed, 16777619);
        }
        rand = mulberry32(seed >>> 0);
      }

  // Fisher–Yates shuffle
      for (let i = items.length - 1; i > 0; i--) {
        const j = Math.floor(rand() * (i + 1));
        [items[i], items[j]] = [items[j], items[i]];
      }

  const frag = document.createDocumentFragment();
      items.forEach(n => frag.appendChild(n));
      container.appendChild(frag);
    }

  function init() {
      document
        .querySelectorAll('.masonry')
        .forEach(g => shuffleNodes(g, MODE));
    }

  if (document.readyState === 'loading') {
      document.addEventListener('DOMContentLoaded', init);
    } else {
      init();
    }
  })();
</script>
